\newcommand{\cvpar}[2]{\makebox[2.5cm][l]{#1}\parbox[t]{12.9cm}{#2}}
\newcommand{\cvref}[2]{\parbox[t]{6.8cm}{#1}\qquad\parbox[t]{8cm}{#2}}
\newcommand{\cvteach}[2]%
  {\makebox[2.4cm][r]{#1}\hspace*{1.1cm}\parbox[t]{11cm}{#2}}
\newcommand{\pp}[0]{{{\raise 2pt\hbox{\scriptsize+}}}}

\pagenumbering{gobble}% Remove page numbers (and reset to 1)
%\input ../summary.tex
%\input motivation.tex
%\newpage

\pagenumbering{arabic}% Arabic page numbers (and reset to 1)

\textbf{\large Blanca MANCILLA} \hfill
\href{https://ca.linkedin.com/in/blancalmancilla/}{\small In LinkedIn }\\
%\textbf{\large Blanca MANCILLA \hfill Curriculum Vitae}\\
%\textbf{\large Blanca MANCILLA }\\

\vspace*{-0.4cm}%
4265, rue Jean-Brillant\\
Montréal (Québec) H3T 1P2, Canada\\
\texttt{+1.514.591.2007}\\
{\it \wordEmail:}
\href{mailto:blancalmancilla@gmail.com}
{\texttt{\small blancalmancilla@gmail.com}}\\
{\it \wordBlog:} \href{https://superspreadsheet.wordpress.com}{\tt{\small superspreadsheet.wordpress.com}}\\
{\it Academic \wordWeb:} \href{http://mancilla.web.cse.unsw.edu.au/}{\tt{\small mancilla.web.cse.unsw.edu.au}}
\qquad \qquad \qquad \qquad 
\begin{pspicture}(1mm,1mm)
%% email or linkedin?
%\psbarcode{MECARD:N:Mancilla,Blanca;TEL:+15145912007;EMAIL:blancalmancilla@gmail.com;URL:http://superspreadsheet.wordpress.com;;}{eclevel=L width=1.15 height=1.15}{qrcode}
\psbarcode{MECARD:URL:https://ca.linkedin.com/in/blancalmancilla/}{eclevel=L width=1.00 height=1.00}{qrcode}
\end{pspicture}

{\it Written, spoken:} English, French, Spanish.\\
{\it Other:} German, B1 level, currently in Goethe Institut.\\


%\vspace*{0.2cm}%
%\subsection*{Professional Profile}
\textbf{\large Professional Profile}

I have +10 years of experience in IT and over a year in Web development. 
I want to use my skills in coding, problem solving, design, writing, 
documentation, formalization, leadership,
lectureship and inter-communication in a development team. 
I am always learning new things, experimenting the latest
technologies or on Twitter.


\thispagestyle{empty}

\vspace*{0.5cm}
\textbf{\large Computer skills snapshot} 
%\subsection*{Computer skills snapshot} 

Web programming in Ruby on Rails, testing, CSS and Bootstrap, HTML.\\ 
Open source development tools, Linux, scripting languages, git,
github, bitbucket, \LaTeX. \\
Teaching knowledge in C, JSP, java, haskell, geographical information
systems, computer graphics, human computer interaction, 
information systems. \\

\input ../current.tex

\vspace*{-0.5cm}
\input ../projects.tex

\vspace*{-0.3cm}
\input ../education.tex

\vspace*{-0.5cm}
\input ../jobs.tex

\vspace*{-0.3cm}
\subsection*{\titleOrganization}
\vspace*{-0.2cm}

\cvpar{2001--2002}{
\emph{International Conference on Distributed Communities on the Web},
\sigla{dcw} 2002 \\
Local Arrangements Chair: Webmaster; budget and conference manager.
}

\cvpar{2000--2002}{
\emph{Women in Computing}, \sigla{unsw} \\
\director: Liaison between community stakeholders; conception of
events.
}

\cvpar{2000--2003}{
\girlsWorkshops
}

%\vspace*{-0.4cm}
%\subsection*{\engagements} 
%\vspace*{-0.2cm}

%Conference reviewer and committee member in 4 venues.\\
%9 \titleInvitedVisits\ in India, Switzerland, France, Canada, Japan,
%Hong Kong.\\
%4 \titleInvitedTalks\ in Germany, Japan, Canada.

\vspace*{0.2cm}
\textbf{\large \titlePublications},~
\href
{http://plaice.web.cse.unsw.edu.au/~plaice/archive/BLM/}
{\texttt{\footnotesize http://plaice.web.cse.unsw.edu.au/\char126plaice/archive/BLM}}

\begin{tabular}{@{}p{1.0cm}r@{\hspace*{2.7cm}}p{4.0cm}r
@{\hspace*{1cm}}p{4.0cm}r }
Total & 28 &
{\pubBooks}&{1}&
{\pubChapters}&{1}\\
&&{\pubJournals}&{5}&
{\pubTheses}&{2}\\
&&{\pubConferences}&{17}&
{\pubCompilations}&{2} \\
\end{tabular}

\endinput

\vspace*{-0.5cm}
\subsection*{Relevant Skills}

%\begin{multicols}{2}{
\begin{minipage}{0.48\textwidth}

\subsubsection*{Simplification of concepts}
\vspace*{-0.2cm}


I have been invited to speak about my work at international venues,
due to my ability to recapitulate and to express complex ideas in a simple
yet concrete way, adjusting 
to different audiences and environments.

\vspace*{.1cm}

In the girls workshops, I introduced the day, with the goal of waking up
the curiosity and interest of a hostile audience.  I simplified my research
to relate to the girls and map their everyday life to technology
advancements. I always succeeded in engaging the group throughout the day
and at the end, they always delivered wonderful results.


\subsubsection*{Conceptualization, synthesis, attention to detail,
rigorous writing}
\vspace*{-0.2cm}


In the preparation of my many publications, I had to make every
word count; topics had to be more rigorous, formalizing concepts, if they
were for journal publication, and more engaging, relating a story, if they
were for conference proceedings. The introductions had to give a concise
overview of the problem showing understanding of the subject.
Data, processes and results analysis were
crucial to allow me to identify problems and propose better solutions and
alternatives.

%I always had to convey the ideas, sometimes
%by concretizing was has been said, others by formalizing concepts, in a
%very clear and consice way, while engaging the audience.

\subsubsection*{Negotiator, facilitator and coordinator}
\vspace*{-0.2cm}

To succeed organizing events around the IT community,
I had to exercise my interpersonal skills to achieve
complicated tasks in tight schedules involving many stakeholders.
My organizational qualities, my lead role and my team work participation
were essential to achieve all the goals running workshops and conferences. 

\vspace*{.1cm}

The academic visits were rewarding:
I developed lasting relationships, received 
research students as visitors and worked on multi-university
projects.
%These were the result of brainstorming sessions, exchange of
%ideas and knowledge and adapting to the culture around me.


\end{minipage}
\hspace*{0.6cm}
\begin{minipage}{0.50\textwidth}

\subsubsection*{Analysis of Processes}
\vspace*{-0.2cm}

I implemented the following process
for the ACMS research software:
%Following is the description of the ACMS software.

\vspace*{.1cm}
{\it Establish the goal:} To create an interactive website from the ground up
using a newly developed programming language which easily manipulates
contexts and versions. 
\vspace*{.1cm}

{\it Study of resources:} Find and evaluate
a geographical mapping tool,
a multilingual typesetter engine,
a contextual DBMS,
and
create a web server
to unite these tools.
\vspace*{.1cm}

{\it Plan and implement:} Study the feasibility of a
multidisciplinary project, with the creation of
flowcharts, work proposals,
time charts, 
presentations for approval,
coding.%
\vspace*{.1cm}

{\it Document and validate:} write final thesis and articles for
publication; test website.

\subsubsection*{Logical thinking and data analysis}
\vspace*{-0.2cm}


I was invited to assess manuscripts and
evaluate their content as worth for publication or presentation, according
to relevance to audience and venue, scope, quality and level of work. 

\vspace*{.1cm}

I have been PhD and research theses advisor, assessor and marker.
I directed students on their work and helped them to completion.




\subsubsection*{Training capabilities, communication}
\vspace*{-0.2cm}

I have taught in different areas to a variety of cultures and ages, in
different languages. I lectured civil, geomatic, computer, software
engineering and information technology students at different universities,
both at under- and post-graduate level.  I have given presentations at
international venues to audiences of varying fields of knowledge and
backgrounds.  I directed groups of primary school children, trained users
on software usage and taught sports to children and adults.  Adaptability
has been the key to success in each of these deliveries, adjusting on the
spot.

%\subsubsection*{Oher qualities}
%\vspace*{-0.2cm}
%
%{Fast learner, enthusiastic, curious, problem solver, crave for
%organization, 
%adaptability to constant change.
%}


%}
%\end{multicols}
\end{minipage}


